Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-25 docs/manuscript/manuscript.tex

Globally, access to improved drinking water sources and sanitation is increasing. From 1990 to 2012, the utilization of
improved drinking water sources has increased globally from 76 percent to 89 percent, and utilization of improved
sanitation has increased from 45 percent to 64 percent \citep{fuller2016tracking}. According to the MDG categorization,
they consider improved drinking water sources as the following: public tap, borehole, protected spring, rainwater
collection, bottled water source, and piped water \citep{bartram2014globala}. However, these variables do not truly
explain if the households have speedy access to retrieve the water. In this paper, we investigate further on what
variables should be included to enhance the accessibility of improved drinking water.

% {\reversemarginpar\marginnote{\scriptsize\rd The introduction should end with a paragraph summarizing the contents and layout of the remainder of the manuscript. E.g. ``In the next section we discuss relevant prior research on water accessibility quantification. Next, we present the data and methods...''}}

In the next section we discuss relevant prior research on water accessibility quantification. We are interested in what type of modes of
transportation are utilized to provide clean and drinking water to the community. Also, we desire to learn more about
the time it takes to transport water to the community in a global modeling context. So that we can develop and quantify
water accessibility in different countries to compare different trends. Also, we will be exploring the most efficient
and effective modes of transportation of accessible water. Therefore, the new models will be able to influence and
encourage policymakers in specific countries to improve water accessibility for all. Next we present the data and methods of approaching the quantification of the water accessibility.

>>>>

Globally, access to improved drinking water sources and sanitation is increasing. From 1990 to 2012, the utilization of
improved drinking water sources has increased globally from 76 percent to 89 percent, and utilization of improved
sanitation has increased from 45 percent to 64 percent \citep{fuller2016tracking}. According to the Millennium Development Goals (MDGs),
they consider improved drinking water sources as the following: public tap, borehole, protected spring, rainwater
collection, bottled water source, and piped water \citep{bartram2014globala}. However, these variables do not truly
explain if the households have speedy access to retrieve the water.

% {\reversemarginpar\marginnote{\scriptsize\rd The introduction should end with a paragraph summarizing the contents and layout of the remainder of the manuscript. E.g. ``In the next section we discuss relevant prior research on water accessibility quantification. Next, we present the data and methods...''}} 
In this paper, we investigate further on what
variables should be included to enhance the accessibility of improved drinking water.
In the next section we discuss relevant prior research on water accessibility quantification. We are interested in what type of modes of
transportation are utilized to provide clean and drinking water to the community. Also, our objective is to investigate
the time it takes to transport water to the community in a global modeling context. So that we can develop and quantify
water accessibility in different countries to compare different trends. Also, we will be exploring the most efficient
and effective modes of transportation of accessible water. Therefore, the new models will be able to influence and
encourage policymakers in specific countries to improve water accessibility for all. Next we present the data and methods of approaching the quantification of the water accessibility.
